Temporal graph realization from fastest paths

### 2024-05-01 Arxiv-30-4-24/arxiv-30-4-24.tex
Changes 1st May 2024

From the above we get the following assumptions:
	\begin{enumerate}
		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
	\end{enumerate}
In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
%%%%%% HM: the following is never used..
%It follows that:
%	\begin{itemize}
%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
%		u$ to $v$.
%	\end{itemize}
%
 Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
	\Delta $ and that $t_{v_2}\leq t_{u_{2}}\leq 2\Delta $. 
    From Assumption~\ref{assumption1-FPT} we get
	\begin{equation*}
		\delta
		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
	\end{equation*}%
	and thus%
	\begin{equation}
		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
		\label{basic-eq-1}
	\end{equation}

@@

	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
		\{v_{i}v_{i-1}\})$.
	\end{lemma}
	\begin{proof}
		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{i}}}(u,v_{i},Q)=x%
		\Delta +e$. Then $A_{t_{v_{i}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
		that $A_{t_{v_{i}}}(u,v_{i},P)=x\Delta +g$.

@@

		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast
		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, \ie $%
		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
		\begin{eqnarray*}
			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta
			+h-(t_{u_{2}}-t_{v_2}) \\
			&\geq &(\Delta -\delta _{0})+h>0,
		\end{eqnarray*}%
		which proves the statement of the lemma.

@@

		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
		A_{t_{v_{i}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
		x\Delta +e-h$, \ie $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
		Summarizing, we have:%
		\begin{equation*}
			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
		\end{equation*}%
		which proves the statement of the lemma.
	\end{proof}

>>>>

From the above we get the following assumptions:
	\begin{enumerate}
		\item \label{assumption1-FPT} $d(u,v_{i})=d(u,v_{i},P)\leq d(u,v_{i},Q)$, and
		\item \label{assumption2-FPT} $d(u,v_p)=d(u,v_p,Q\cup R)\leq d(u,v_p,P\cup R)$.
	\end{enumerate}
In the remainder, we denote with $\delta_{0}$ the difference $d(u,v_{i},Q) - d(u,v_{i})\geq 0$.
%%%%%% HM: the following is never used..
%It follows that:
%	\begin{itemize}
%		\item $A_{t}(u,v,P)=t_{0}+d(u,v,P)-1$, for every $u,v$, where $t_{0}\in
%		\lbrack t,t+\Delta -1]$ is the label of the first edge of the path $P$ from $%
%		u$ to $v$.
%	\end{itemize}
%
 Let $t_{v_2}\in [\Delta]$ be the label of the edge $uv_2$,
	and denote by $t_{u_{2}}$ the appearance of the edge $uu_{2}$ within the
	period $[t_{v_2},t_{v_2}+\Delta -1]$. Note that $1\leq t_{v_2}\leq
	\Delta $ and that 
 \begin{equation}
t_{v_{2}} \leq t_{u_{2}} \leq t_{v_{2}}+\Delta -1 \leq 2\Delta -1.
\label{basic-ineq-0}
\end{equation}
    From Assumption~\ref{assumption1-FPT} we get
	\begin{equation*}
		\delta
		_{0}=d(u,v_{i},Q)-d(u,v_{i})=A_{t_{v_2}}(u,v_{i},Q)-A_{t_{v_2}}(u,v_{i},P)+\left( t_{u_{2}}-t_{v_2}\right)
	\end{equation*}%
	and thus%
	\begin{equation}
		A_{t_{v_2}}(u,v_{i},P)-A_{t_{v_2}}(u,v_{i},Q)=t_{u_{2}}-(t_{v_2}+\delta _{0}).
		\label{basic-eq-1}
	\end{equation}

@@

	\begin{lemma}\label{lemma:FPT-twoPathsOneUnlabeledEdge}
		\label{lem-2}$d(u,v_{i-1},P\cup \{v_{i}v_{i-1}\})>d(u,v_{i-1},Q\setminus
		\{v_{i}v_{i-1}\})$.
	\end{lemma}
	\begin{proof}
		Let $e\in [\Delta]$ be the label of the edge $v_{i-1}v_{i}$, and
		let $f\in \lbrack e+1,e+\Delta ]$ be the time of the first appearance of the
		edge $v_{i}v_{i+1}$ after time $e$. Let $A_{t_{v_{2}}}(u,v_{i},Q)=x%
		\Delta +e$. Then $A_{t_{v_{2}}}(u,v_{i+1},Q\cup\{v_{i}v_{i+1}\})=x\Delta +f$. Furthermore let $g$ be such
		that $A_{t_{v_{2}}}(u,v_{i},P)=x\Delta +g$.

@@

		Now consider the path $Q^{\ast }=Q\setminus \{v_{i}v_{i-1}\}$. Let $h\in
		\lbrack 1,\Delta ]$ be such that $A_{t_{v_{2}}}(u,v_{i-1},Q^{\ast
		})=x\Delta +e-h$. That is, if we start traversing $Q^{\ast }$
		at time $t_{v_2}$, we arrive at $v_{i-1}$ at time $x\Delta +e-h$, \ie $%
		d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_2}+1$. Summarizing, we have:%
		\begin{eqnarray*}
			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast }) &=&\Delta +h-(t_{u_{2}}-t_{v_2}) \\
			&\geq & \Delta +1-(\Delta-1)>0,
		\end{eqnarray*}%
		where the last inequality follows by (\ref{basic-ineq-0}). This proves the statement of the lemma.

@@

		Similarly to Case 1, let $h\in \lbrack 1,\Delta ]$ be such that $%
		A_{t_{v_{2}}}(u,v_{i-1},Q^{\ast })=x\Delta +e-h$. That is, if we start
		traversing $Q^{\ast }$ at time $t_{v_{2}}$, we arrive at $v_{i-1}$ at time $%
		x\Delta +e-h$, \ie $d(u,v_{i-1},Q^{\ast })=x\Delta +e-h-t_{v_{1}}+1$.
		Summarizing, we have:%
		\begin{equation*}
			d(u,v_{i-1},P^{\ast })-d(u,v_{i-1},Q^{\ast })\geq h\geq 1,
		\end{equation*}%
		which proves the statement of the lemma.
	\end{proof}
